---
title: "Final Project RMarkdown"
author: "Angela Yu"
date: "`r Sys.Date()`"
output: html_document
params:
  production: TRUE
---

```{r, set-chunk-opts, echo = FALSE, eval = params$production}
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```

# Introduction

The dataset comes from the PAMAP2 Physical Activity Monitoring dataset, which originally comprised data from 18 different physical activities (such as walking, cycling, playing soccer, etc.) performed by 9 subjects wearing 3 inertial measurement units and a heart rate monitor.

In this Rmarkdown file, I analyzed the data from Subject 1, and restricted the activities to lying, sitting, standing and walking. The interested variables are hear rate and hand temperature.

I made a table to show the variation of the interested variables between different activity groups, and I also plot their trends across time for all groups.

```{r, load-data}
here::i_am("Final_Project_RMarkdown.Rmd")
data <- readRDS(
  file = here::gihere("output/data_clean.rds")
)
```

# Descriptive Analysis

## Tabular analysis

This table provides a summary of the distribution of heart rate and hand temperature across different activity groups.

```{r, table1}
table <- readRDS(
  file = here::here("output/table.rds")
)
```

## Figure analysis

This image visualizes the heart rate variations under different activityID categories (lying, sitting, standing, walking).
The X-axis is Time, and the Y-axis is heart rate values.
Each activity is plotted in a distinct color and accompanied by a dashed trend line.
From this plot, we can see that the average heart rate tends to drop when physical activity's strength decreases.

```{r, plot-data}
#| fig.align = "center",
#| out.width = "600px"
knitr::include_graphics(
  here::here("output/series_plot.png")
)
```